### 2022-12-02 definitions.tex
details

\begin{theorem}
{\sc resilience} is undecidable for WSTS (with upward compatibility).
\end{theorem}

\begin{proof}
on choisit $J=Reach(S)$. resilience remains to {$\forall s \in S,  \exists s'' \in I ~ s' \rightarrow^{*} s''$ ?\newline}. il existe un chemin infini passant par inft par $q$, liveness undecidable LCS (Reach=$\downarrow Reach$), Reset, WSTS.
\end{proof}

>>>>

Unfortunately, resilience is undecidable for general WSTS even with strong monotony.

\begin{theorem}
{\sc resilience} is undecidable for WSTS with strong monotony.
\end{theorem}

\begin{proof}
Let $J=\downarrow Reach(S)$. Now resilience remains to the following property: $\forall s \in S,  \exists s'' \in I, ~ s' \rightarrow^{*} s''$. This property is a liveness property that would allow to decide LTL but LTL has been proved undecidable for Lossy Channel Systems (LCS) for which Reach=$\downarrow Reach$.
Since LCS are effective WSTS with strong monotony (with an adequate semantics), we conclude.
\end{proof}

Since Reset Petri nets are also effective WSTS with strong monotony, we could think to use the undecidability of LTL for Reset Petri nets but $Reach \neq \downarrow Reach$.
